---
title: "R Notebook"
output: html_notebook
---

# Load Data

```{r}
library(tidyverse)
```

```{r}
jeopardy_df <- read_csv("../data/raw/jeopardy.csv")
jeopardy_df
```

# Filter to Daily Doubles

There is no indicator column for Daily Doubles. Instead, to find most of the Daily Doubles, we'll filter out the "standard" Jeopardy scores and remove Final Jeopardy questions.

```{r}
standard_values <- c(
  200, 400, 600, 800, 1000,
  1200, 1600, 2000
)

filtered_jeopardy_df <- jeopardy_df %>%
  filter(!(value %in% standard_values),
         value > 0,
         round != "Final Jeopardy!")

filtered_jeopardy_df
```

```{r}
filtered_jeopardy_df %>%
  saveRDS("../data/processed/filtered_jeopardy_df.rds")
```

# Clean Text

There are three main steps:

-   Lowercase all letters

-   Keep only letters (remove numbers and punctuation)

-   Remove stopwords

```{r}
library(tm)
library(tidytext)
```

```{r}
filtered_jeopardy_df <- readRDS("../data/processed/filtered_jeopardy_df.rds")
filtered_jeopardy_df
```

```{r}
cleaned_jeopardy_df <- filtered_jeopardy_df %>%
  mutate(
    question = tolower(question),
    answer = tolower(answer),
    category = tolower(category)
  )

cleaned_jeopardy_df
```

```{r}
cleaned_jeopardy_df <- cleaned_jeopardy_df %>%
  mutate(
    question = gsub("([^a-z ])+", "", question),
    answer = gsub("([^a-z ])+", "", answer),
    category = gsub("([^a-z ])+", "", category)
  )

cleaned_jeopardy_df
```

```{r}
cleaned_jeopardy_df <- cleaned_jeopardy_df %>%
  mutate(
    question = removeWords(question, stopwords()),
    answer = removeWords(answer, stopwords()),
    category = removeWords(category, stopwords())
  )

cleaned_jeopardy_df
```

```{r}
cleaned_jeopardy_df %>%
  saveRDS("../data/processed/cleaned_jeopardy_df.rds")
```

# Calculate Scrabble Scores

Next, we calculate the average scrabble score of the words in all questions, answers, and categories.

```{r}
# https://quanteda.io/reference/textstat_readability.html
library(quanteda.textstats)
```

```{r}
cleaned_jeopardy_df <- readRDS("../data/processed/cleaned_jeopardy_df.rds")
cleaned_jeopardy_df
```

```{r}
scrabble_jeopardy_df <- cleaned_jeopardy_df %>%
  mutate(
    question_scrabble_score = textstat_readability(question, measure = "Scrabble")$Scrabble,
    answer_scrabble_score = textstat_readability(answer, measure = "Scrabble")$Scrabble,
    category_scrabble_score = textstat_readability(category, measure = "Scrabble")$Scrabble
  )

scrabble_jeopardy_df
```

```{r}
scrabble_jeopardy_df <- scrabble_jeopardy_df %>%
  select(round, value, question_scrabble_score, answer_scrabble_score, category_scrabble_score) %>%
  drop_na()

scrabble_jeopardy_df
```

```{r}
scrabble_jeopardy_df %>%
  saveRDS("../data/processed/scrabble_jeopardy_df.rds")
```

# Analysis

```{r}
library(GGally)
library(corrr)
```

```{r}
scrabble_jeopardy_df <- readRDS("../data/processed/scrabble_jeopardy_df.rds")
scrabble_jeopardy_df
```

```{r}
scrabble_jeopardy_df %>%
  ggpairs(progress = FALSE)
```

```{r}
ggsave(
  filename = "pairs.png",
  device = "png",
  path = "../plots",
  width = 28,
  height = 16,
  units = "in"
)
```

```{r}
cor.test(
  x = scrabble_jeopardy_df$value, 
  y = scrabble_jeopardy_df$question_scrabble_score, 
  alternative = "two.sided", 
  method = "kendall", 
  conf.level = 0.95
)
```

```{r}
scrabble_jeopardy_df %>%
  filter(value > 500)
```
